---
output: github_document
---

# Run reconstruction for Skeena River Chinook, 1984-2024


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%"
)
h <- 6
w <- 6
```

## Purpose

<!-- badges: start -->
<!-- badges: end -->

The goal of **skrunchy2025** is to update the run reconstruction for Skeena River Chinook salmon for years 1984-2024. This file does this analysis and save results into the [data](data/) folder. It uses cleaned data in the [data](data/) folder and the functions from the [skrunchy](https://github.com/Pacific-salmon-assess/skrunchy) package. 

See package [skrunchy](https://github.com/Pacific-salmon-assess/skrunchy) - **Sk**eena River **Run** Reconstruction for **Ch**inook Salmon - for detailed methods and functions. 
The goal of skrunchy is to recreate and update the run reconstruction for Skeena River summer run timing Chinook upstream of Tyee test fishery (aggregate plus six Conservation Units), as documented in [Winther et al. 2024](https://publications.gc.ca/site/eng/9.901355/publication.html "An assessment of Skeena River Chinook salmon using genetic stock identification 1984 to 2020").

[This methods document](https://github.com/Pacific-salmon-assess/skrunchy/blob/1296a4d8effdc5d75e464436b5d2861e2915f3bf/methods.pdf) contains detailed methods, variables, and equations matching this package as much as possible. 

### Why two packages?

[skrunchy2025](https://github.com/lukewarkentin/skrunchy2025) is like the sandbox with all the data for 1984-2024, and  [skrunchy](https://github.com/Pacific-salmon-assess/skrunchy) is like the toolbox that has all the functions to do the run reconstruction ([see this post by Dr. Stephanie C. Hicks](https://www.stephaniehicks.com/blog/why-it-s-best-to-keep-software-and-data-analysis-repositories-separate/)). That way, every time we do an actual data update of the run reconstruction, we don’t have to further complicate the skrunchy software package.

## General methods

Here, we take a known abundance of population (in this case, Kitsumkalum) $K$ and expand it to estimate an aggregate population size $X_{aggregate}$ using the proportion of fish from population $K$ in a mixed genetic sample, $P_K$: 

$$X_{aggregate} = \frac{K}{P_K}$$

Further, the abundance of other populations $X_i$ can be estimated using their genetic proportion $P_i$ and the aggregate abundance $X_{aggregate}$: 

$$X_i = X_{aggregate} \cdot P_i$$

After that, the run is "reconstructed": working backwards from age-specific wild spawner abundance, all mortalities (brood stock removals, fishery harvest, incidental mortality) are added back in, to estimate the total run (escapement plus all mortality). From total run, we calculate recruits by brood year, which can then be use to model productivity. 


## Run Reconstruction 

We can walk through all the functions with data saved in the [data](data/) folder

Note that most of the package functions produce lists with two elements. The first element is an array, and the second element is a data frame. The array is used for subsequent analysis, and the data frame is useful for plotting and producing report tables. 

```{r libs}
library(skrunchy)
library(ggplot2)
library(latex2exp)
library(here)
library(dplyr)
options(scipen = 999)
# Load all files in data/ folder
devtools::load_all(".") # could probably replace this with library(skrunchy2025) but would need to reinstall to reflect any updates. 
```


Use example data from Skeena Tyee test fishery weekly catch and genetic mixture data, and pool it into annual genetic proportions. 


```{r P_tilde, dpi=300}
P_tilde <- get_P_tilde(P = P, sigma_P = sigma_P, G = G)

ggplot( P_tilde$df, aes(y = P_tilde, x = y, group = i)) +
  geom_errorbar( aes( ymin = P_tilde - sigma_P_tilde, ymax = P_tilde + sigma_P_tilde ), colour="dodgerblue") +
  geom_point() +
  geom_line() +
  facet_wrap(~i, ncol=2) +
  ylab(TeX("$\\tilde{P}$")) +
  geom_hline(aes(yintercept=0)) +
  theme_classic() 
  
```

Now do expansions to get returns to Terrace for each population, and the Skeena aggregate.

```{r X, dpi = 300 }
k <- kitsumkalum[ kitsumkalum$year <= 2024, ]
X <- get_X(P_tilde = P_tilde$P_tilde, sigma_P_tilde = P_tilde$sigma_P_tilde, K= k$kitsumkalum_escapement, 
           sigma_K = k$sd,
           y_K = k$year)

ggplot( X$df, aes(y = X, x = y, group = i)) +
  geom_errorbar( aes( ymin = X - sigma_X, ymax = X + sigma_X)) +
  geom_point() +
  geom_line() +
  facet_wrap(~i, ncol=2, scales = "free_y") +
  geom_hline(aes(yintercept=0)) +
  theme_classic()
  
```

Estimate terminal mortalities, total by year

Get age proportions by age, population and year, including jacks.

Note higher jack proportion in recent years. 

```{r omega_J, dpi = 300 , fig.width = w,fig.height=h/2}
omega_J_all <- omega_J
omega_J_skeena <- omega_J$omega["Skeena",,] # only include Skeena

ggplot( omega_J_all$df[ omega_J_all$df$i == "Skeena", ], aes(y = omega, x = y, group = i)) +
  geom_point() + 
  geom_line() + 
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$\\Omega_J$") )+
  facet_grid( i ~ a ) + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))

```

Get freshwater terminal mortalities in the lower Skeena by year
```{r Tau_L_total, dpi = 300 , fig.width = w,fig.height=h/2}

Tau_L_total <- get_Tau_L_total( omega_J = omega_J_skeena, tyee = Tau$tyee, 
                                rec_catch_L = Tau$rec_catch_L,
                                rec_release_L = Tau$rec_release_L, 
                                FN_catch_L = Tau$FN_catch_L)

Tau_L_total_df <- data.frame( "Tau_L_total" = Tau_L_total, y = as.integer(names(Tau_L_total)))

ggplot( Tau_L_total_df, aes(y = Tau_L_total, x = y, group = 1)) +
  geom_line() + 
  geom_point() + 
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$T_L$") )+
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))
```

Get freshwater terminal mortalities in the upper Skeena by year
```{r Tau_U_total, dpi = 300 , fig.width = w,fig.height=h/2}
Tau_U_total <- get_Tau_U_total( omega_J = omega_J_skeena, rec_catch_U = Tau$rec_catch_U,
                                   FN_catch_U = Tau$FN_catch_U)
Tau_U_total_df <- data.frame(Tau_U_total, y = as.integer(names(Tau_U_total) ))
ggplot( Tau_U_total_df, aes(y = Tau_U_total, x = y, group = 1)) +
  geom_point() + 
  geom_line() + 
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$T_U$") )+
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))

```

Get escapement for each population, plot with returns to Terrace (note, will only be different for Skeena aggregate and the three upper populations). See below for $T_U$ calculations.

```{r E, dpi = 300 }
E <- get_E(K = k$kitsumkalum_escapement, X = X$X, Tau_U = Tau_U_total,
     known_population = "Kitsumkalum",
     aggregate_population = "Skeena",
     lower_populations = c("Lower Skeena", "Zymoetz"),
     upper_populations = c("Upper Skeena", "Middle Skeena", "Large Lakes"))

ggplot(X$df, aes(y = X, x = y, group = i)) +
  geom_errorbar( aes( ymin = X - sigma_X, ymax = X + sigma_X)) +
  geom_point() +
  geom_line() +
  geom_line(data = E$df, aes(y = E, x = y, group=i), colour="gray") +
  facet_wrap(~i, ncol=2, scales = "free_y") +
  ylab("Return to Terrace (X) in black, escapement (E) in gray") +
  geom_hline(aes(yintercept=0)) +
  theme_classic()

```

Get age proportions by age, population and year (fake data).

```{r omega, dpi = 300 , fig.width = w,fig.height=h}
omega <- omega

ggplot( omega$df, aes(y = omega, x = y, group = i)) +
  geom_point() + 
  geom_line() + 
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$\\Omega$") )+
  facet_grid( i ~ a ) + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))

```

Get age-specific escapement for Kitsumkalum River, from sex-specific age proportions, sex-specific escapement, and hatchery contributions. 

```{r K_star, dpi = 300, fig.width = w, fig.height=h}
K_star <- K_star
K_star_df <- array2DF( K_star, responseName = "K_star")
# K_star <- get_K_star( K = k$kitsumkalum_escapement, y_K = k$year, 
#                       K_M = k$male_escapement, K_F = k$female_escapement, 
#                       omega_KM = omega_K[ "M",,  ], omega_KF = omega_K[ "F",, ], 
#                       H = H, H_star = H_star)

ggplot(K_star_df, aes(y = K_star, x = y, group= a )) +
  geom_point() +
  geom_line() +
  facet_wrap(~a, ncol=2 ) +
  ylab(TeX("Kitsumkalum escapement by age ($K^*$)") ) +
  geom_hline(aes(yintercept=0)) +
  theme_classic()

```


Get age-specific escapement by using age proportions. 

```{r E_star, dpi=300, fig.width = w,fig.height=h}
E_star <- get_E_star(E = E$E, omega = omega$omega, K_star = K_star, add_6_7 = TRUE)

ggplot( E_star$df, aes(y = E_star, x = y, group = i)) +
  geom_point( colour="gray") + 
  geom_line( colour="gray") + 
  geom_hline(aes(yintercept=0)) + 
  facet_grid( i ~ a , scales = "free_y") + 
  ylab("Escapement (E*)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))
```

Get spawners for each population (accounts for brood stock removals), plot with returns to Terrace and escapement. Spawners should only be different from escapement for Skeena aggregate and Kitsumkalum, since brood removals are only for Kitsumkalum.

```{r S_star, dpi = 300, fig.width = w,fig.height=h }
S_star <- get_S_star(E_star = E_star$E_star, B_star = B_star)

ggplot( E_star$df, aes(y = E_star, x = y, group = i)) +
  geom_point(colour="gray") + 
  geom_line(colour="gray") + 
  geom_line(data = S_star$df, aes(y = S_star, x = y, group = i), colour="dodgerblue") +
  geom_hline(aes(yintercept=0)) + 
  facet_grid( i ~ a , scales = "free_y") + 
  ylab("Escapement (E*) in gray and spawners (S*) in blue") +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))

```

Get wild spawners for each population (accounts for hatchery origin spawners), plot with returns to Terrace, escapement, and spawners. Wild spawners should only be different from spawners for Skeena aggregate and Kitsumkalum, since hatchery origin spawners only occur for Kitsumkalum.


```{r W_star, dpi = 300, fig.width = w,fig.height=h }
W_star <- get_W_star( S_star = S_star$S_star, H_star = H_star) 

ggplot( E_star$df, aes(y = E_star, x = y, group = i)) +
  geom_point(colour="gray") + 
  geom_line(colour="gray") + 
  geom_line(data = W_star$df, aes(y = W_star, x = y, group = i), colour="firebrick") +
  geom_line(data = S_star$df, aes(y = S_star, x = y, group = i), colour="dodgerblue") +
  geom_hline(aes(yintercept=0)) + 
  facet_grid( i ~ a , scales = "free_y") + 
  ylab("Escapement (E*) in gray, spawners (S*) in blue,\nand wild spawners (W*) in red.") +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))

```

Get proportion wild spawners for each population and plot. Should only be <1 for Skeena aggregate and Kitsumkalum, since hatchery origin spawners only occur for Kitsumkalum. Note this is not real data, p is very high for Kitsumkalum across years. 


```{r p, dpi = 300 , fig.width = w,fig.height=h}
p <- get_p(W_star = W_star$W_star, E_star = E_star$E_star, B_star = B_star)

# # replace values of p = 0, in 1994, 1996, for Kitsumkalum
# p$p["Kitsumkalum", as.character(c(1994, 1996)),"4" ] <- mean( p$p["Kitsumkalum", as.character(c(1984:1993,1995,1997:2024)),"4" ] )
# p$df$p[ p$df$p == 0 ] <-  mean( p$p["Kitsumkalum", as.character(c(1984:1993,1995,1997:2024)),"4" ] )

ggplot(p$df, aes(y = p, x = y, group = i)) +
  geom_point() +
  geom_line() +
  facet_grid(i~a) +
  ylab("Proportion wild spawners, p") +
  geom_hline(aes(yintercept=0)) +
  theme_classic()+
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))

```

Estimate freshwater terminal mortalities in the lower Skeena by population, year, and age. 


```{r tau_L, dpi = 300 , fig.width = w,fig.height=h}
tau_L <- get_tau_L(Tau_L = Tau_L_total, omega = omega$omega, P_tilde = P_tilde$P_tilde, aggregate_population = "Skeena", add_6_7 = TRUE)

ggplot( tau_L$df , aes(y =tau_L, x = y, group = i)) +
  geom_point() + 
  geom_line() + 
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$\\tau_L$")) +
  facet_grid( i ~ a, scales="free_y") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))
```

Estimate freshwater terminal mortalities in the upper Skeena by population, year, and age. Should be 0 for Kitsumkalum, Lower Skeena, and Zymoetz-Fiddler. 


```{r tau_U, dpi = 300, fig.width = w,fig.height=h }
tau_U <- get_tau_U(Tau_U = Tau_U_total, omega = omega$omega, P_tilde = P_tilde$P_tilde, aggregate_population = "Skeena",
                   upper_populations = c("Middle Skeena", "Large Lakes", "Upper Skeena"),
    lower_populations = c("Lower Skeena", "Kitsumkalum", "Zymoetz"), add_6_7 = TRUE)

ggplot( tau_U$df, aes(y =tau_U, x = y, group = i)) +
  geom_point() + 
  geom_line() + 
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$\\tau_U$")) +
  facet_grid( i ~ a) + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))
```

Estimate marine terminal mortalities in the marine area by population, year, and age. 


```{r tau_M, dpi = 300 , fig.width = w,fig.height=h}
tau_M <- get_tau_M( W_star = W_star$W_star, tau_dot_M = tau_dot_M)

ggplot( tau_M$df, aes(y =tau_M, x = y, group = i)) +
  geom_point() + 
  geom_line() + 
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$\\tau_M$")) +
  facet_grid( i ~ a, scales="free_y") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))
```

<!-- Get total terminal mortality  -->

<!-- ```{r tau, dpi=300, fig.width = w,fig.height=h} -->
<!-- tau <- get_tau(tau_U = tau_U$tau_U, tau_L = tau_L$tau_L, tau_M= tau_M$tau_M) -->

<!-- ggplot( tau$df, aes(y =tau, x = y, group = i)) + -->
<!--   geom_line() + -->
<!--   geom_point() + -->
<!--   geom_line( data = tau_L$df, aes(y =tau_L, x = y), colour="goldenrod") + -->
<!--   geom_line( data = tau_U$df, aes(y =tau_U, x = y), colour="aquamarine") + -->
<!--   geom_line( data = tau_M$df, aes(y =tau_M, x = y), colour="blue") + -->
<!--   geom_hline(aes(yintercept=0)) +  -->
<!--   ylab(TeX("$\\tau$")) + -->
<!--   facet_grid( i ~ a, scales="free_y") +  -->
<!--   theme_classic() + -->
<!--   theme(axis.text.x = element_text(angle=90, vjust=0.5), -->
<!--         strip.text.y = element_text(angle = 0)) -->

<!-- ``` -->


Get wild total terminal mortality 

```{r tau_W, dpi=300, fig.width = w,fig.height=h}
tau_W <- get_tau_W(tau_U= tau_U$tau_U, tau_L = tau_L$tau_L, tau_M = tau_M$tau_M, p = p$p)

ggplot( tau_W$df, aes(y =tau_W, x = y, group = i)) +
  geom_line() +
  geom_point() +
  geom_hline(aes(yintercept=0)) + 
  geom_line( data = tau_L$df, aes(y =tau_L, x = y), colour="goldenrod") + 
  geom_line( data = tau_U$df, aes(y =tau_U, x = y), colour="aquamarine") + 
  geom_line( data = tau_M$df, aes(y =tau_M, x = y), colour="blue") + 
  ylab(TeX("$\\tau_W$ in black")) +
  facet_grid( i ~ a, scales="free_y") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))


```


Get wild terminal run 

```{r TermRun, dpi=300, fig.width = w,fig.height=h}
TermRun <- get_TermRun(tau_W = tau_W$tau_W, W_star = W_star$W_star, B_star = B_star)

ggplot( TermRun$df, aes(y =TermRun, x = y, group = i)) +
  geom_line() +
  geom_point() +
  geom_line( data = tau_W$df, aes(y =tau_W, x = y), colour="darkorange3") +
  geom_line( data = W_star$df, aes(y =W_star, x = y), colour="firebrick") +
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$TermRun$ in black, $\\tau_W$ in orange, and $W^*$ in red")) +
  facet_grid( i ~ a, scales="free_y") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))


```

Get mature run 

```{r MatureRun, dpi=300, fig.width = w,fig.height=h}
MatureRun <- get_MatureRun(TermRun = TermRun$TermRun, phi_dot_M = phi_dot_M)

ggplot( MatureRun$df, aes(y =MatureRun, x = y, group = i)) +
  geom_line(colour="darkgreen") +
  geom_point(colour ="darkgreen") +
  geom_line( data = TermRun$df, aes(y =TermRun, x = y, group = i), colour="black") +
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$MatureRun$ in green, $TermRun$ in black")) +
  facet_grid( i ~ a, scales="free_y") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))


```

Pre-terminal post fishery abundance. 

```{r A_phi, dpi=300, fig.width = w,fig.height=h}
# Quick fix for r, age 4, year = 2003, very low
r[ "2003", "4"] <- mean(r [ as.character(c(2001:2002, 2004:2005)) , "4"])
A_phi <- get_A_phi( MatureRun = MatureRun$MatureRun, r = r)

ggplot( MatureRun$df, aes(y =MatureRun, x = y, group = i)) +
  geom_line(colour="darkgreen") +
  geom_point(colour ="darkgreen") +
  geom_line( data = A_phi$df, aes(y =A_phi, x = y, group = i), colour="dodgerblue") +
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("$MatureRun$ in green, $A_\\varphi$ in blue")) +
  facet_grid( i ~ a, scales="free_y") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))


```
Pre-fishery ocean abundance. 

```{r A_P, dpi=300, fig.width = w,fig.height=h}
A_P <- get_A_P( A_phi = A_phi$A_phi, phi_dot_E = phi_dot_E)

ggplot( A_phi$df, aes(y = A_phi, x = y, group = i)) +
  geom_line(colour="dodgerblue") +
  #geom_point(colour ="dodgerblue") +
  geom_line( data = A_P$df, aes(y =A_P, x = y, group = i), colour="darkorange") +
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("Pre-fishery ocean abundance $A_P$ in orange, $A_\\varphi$ in blue")) +
  facet_grid( i ~ a, scales="free_y") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))


```

Preterminal fishing mortality in nominal fish. 

```{r phi_N, dpi=300, fig.width = w,fig.height=h}
phi_N <- get_phi_N( A_P = A_P$A_P, A_phi = A_phi$A_phi)

ggplot( phi_N$df, aes(y = phi_N, x = y, group = i)) +
  geom_line() +
  geom_point() +
  geom_hline(aes(yintercept=0)) + 
  ylab(TeX("Preterminal fishing mortality in nominal fish, $\\varphi_N$")) +
  facet_grid( i ~ a, scales="free_y") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text( angle = 0))


```

Preterminal fishing mortality in adult equivalents. 
```{r phi_Q, dpi=300, fig.width = w,fig.height=h}
phi_Q <- get_phi_Q( phi_N = phi_N$phi_N, Q = Q)

ggplot( phi_N$df, aes(y = phi_N, x = y, group = i)) +
  geom_line() +
  geom_point() +
  geom_line(data = phi_Q$df, aes( y= phi_Q, x = y), colour="darkorchid1")+
  geom_hline(aes(yintercept=0)) +
  ylab(TeX("Preterminal fishing mortality in adults equivalents $\\varphi_Q$ in purple. $\\varphi_N$ in black")) +
  facet_grid( i ~ a, scales="free_y") +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))


```

Recruits by return year and brood year. 

```{r R_star, dpi=300, fig.width = w,fig.height=h}
R_star <- get_R_star( MatureRun = MatureRun$MatureRun, phi_Q = phi_Q$phi_Q)

ggplot( R_star$df, aes(y = R_star, x = y, group = i)) +
  geom_line() +
  geom_point() +
  geom_line(data = phi_Q$df, aes( y= phi_Q, x = y), colour="darkorchid1")+
  geom_line(data = MatureRun$df, aes(y = MatureRun, x = y), colour = "darkgreen") +
  geom_hline(aes(yintercept=0)) +
  ylab(TeX("$R^*$ in black, $MatureRun$ in green, $\\varphi_Q$ in pink")) +
  facet_grid( i ~ a, scales="free_y") +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))

ggplot( R_star$df, aes(y = R_star, x = b, group = i, colour= complete_brood)) +
  geom_line() +
  geom_point() +
  geom_hline(aes(yintercept=0)) +
  xlab("Brood year") +
  ylab(TeX("$R^*$ by brood year.")) +
  facet_grid( i ~ a, scales="free_y") +
  scale_colour_manual(values = c("gray", "black")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5),
        strip.text.y = element_text(angle = 0))

```


Get recruits by brood year, summed across ages.
```{r R, dpi=300}
R <- get_R( R_star_b = R_star$R_star_b, R_star_df = R_star$df)

ggplot( R$df, aes(y = R, x = b, group = i, colour = complete_brood)) +
  geom_line() +
  geom_point() +
  geom_hline(aes(yintercept=0)) +
  ylab(TeX("Recruits, $R$")) +
  xlab("Brood year") +
  facet_wrap( ~i , scales="free_y") +
  scale_colour_manual(values = c("gray", "black")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5))


```


```{r save_data }



# Save generated data files to data/ folder
usethis::use_data(P_tilde, overwrite= TRUE)
usethis::use_data(X, overwrite = TRUE)
usethis::use_data(W_star, overwrite = TRUE)
usethis::use_data(R_star, overwrite = TRUE)





```


```{r combine-data-table}

# Merge all data frames by the return year, age, and CU

combine_df_list <- function(x, includes_ages = TRUE) { 
  
  # remove brood year column before merging
  dn <- lapply(x, function(i) {
    df_new <- i[ , !grepl("^b$", names(i))]
    df_new
  } )
  
  if( includes_ages == TRUE) {
  combdf <- Reduce(function(d1, d2) {
    merge(d1, d2, by = c("y", "a", "i"), all = TRUE)
  }, dn)
    combdf$a <- as.integer(combdf$a)
    combdf$y <- as.integer(combdf$y)
    combdf$b <- combdf$y - combdf$a
  }
  
  if( includes_ages == FALSE) {
  combdf <- Reduce(function(d1, d2) {
    merge(d1, d2, by = c("y", "i"), all = TRUE)
  }, dn)
  }

  
  return(combdf)
}

# Make a data frame with brood stock removals, equal for Skeena and Kitsumkalum, 0 for all other CUs
B_star_df <-  array2DF( B_star, responseName = "B_star")

brood_pops <- c("Kitsumkalum", "Skeena")
CU_dummy <-  expand.grid( brood_pops, unique(B_star_df$y), unique(B_star_df$a) ) 
names(CU_dummy) <- c("i", "y", "a")
CU_dummy2 <-  expand.grid( unique(X$df$i)[ !unique(X$df$i) %in% brood_pops], unique(B_star_df$y), unique(B_star_df$a) ) 
names(CU_dummy2) <- c("i", "y", "a")
CU_dummy2$B_star <- 0

B_star_df1 <- merge(B_star_df, CU_dummy, by = c("y", "a"), all = TRUE)
B_star_df2 <- rbind( B_star_df1, CU_dummy2)
# ggplot( B_star_df2, aes ( y = B_star, x  = y)) + 
#   geom_line()+ geom_point() + 
#   facet_grid( i ~ a) + 
#   theme_classic() 

# same for H_star
H_star_df <-  array2DF( H_star, responseName = "H_star")

brood_pops <- c("Kitsumkalum", "Skeena")
CU_dummy <-  expand.grid( brood_pops, unique(H_star_df$y), unique(H_star_df$a) ) 
names(CU_dummy) <- c("i", "y", "a")
CU_dummy2 <-  expand.grid( unique(X$df$i)[ !unique(X$df$i) %in% brood_pops], unique(H_star_df$y), unique(H_star_df$a) ) 
names(CU_dummy2) <- c("i", "y", "a")
CU_dummy2$H_star <- 0

H_star_df1 <- merge(H_star_df, CU_dummy, by = c("y", "a"), all = TRUE)
H_star_df2 <- rbind( H_star_df1, CU_dummy2)
# ggplot( H_star_df2, aes ( y = H_star, x  = y)) +
#   geom_line()+ geom_point() +
#   facet_grid( i ~ a) +
#   theme_classic()




list_df_iya <- list(
                 # omega$df,
                 #"n" = n # n age observations, would need to make into df
                 E_star$df, 
                 B_star_df2,
                 S_star$df,
                 H_star_df2,
                 W_star$df,
                 p$df,
                 tau_L$df,
                 tau_U$df,
                 tau_M$df,
                 tau_W$df,
                 TermRun$df,
                 MatureRun$df,
                 A_phi$df,
                 A_P$df,
                 phi_N$df,
                 phi_Q$df,
                 R_star$df )

#debugonce(combine_df_list)
dc <- combine_df_list(list_df_iya, includes_ages = TRUE)

list_df_iy <- list( P_tilde$df,
                        X$df, 
                        E$df)
#debugonce(combine_df_list)
dciy <- combine_df_list(list_df_iy, includes_ages = FALSE)


# ERA_l <- ERA_w %>% pivot_longer(., cols = 3:8, names_to = "var", values_to = "value")
# ERA_data_processed <- list( df_wide = ERA_w, df_long = ERA_l)
#names(ERA_data_processed)

dc$total_harvest_estimate <- dc$R_star - dc$W_star - dc$B_star
dc$N <- dc$R_star
dc <- dc[ !grepl("R_star", names(dc))] 

# merge ERA rates with run recon table
#names(ERA_data_processed$df_wide)

dc <- merge(dc, ERA_data_processed$df_wide[ !grepl("H_star", names(ERA_data_processed$df_wide)) ], by= c("y", "a", "b"), all.x = TRUE)

#variable_name_key

new_names <- names(dc)
for( i in 1:length(names(dc))) {
  new_names[i] <- ifelse( names(dc)[i] %in% variable_name_key$skrunchy,
                          variable_name_key$skrunchy_with_detail[ variable_name_key$skrunchy == names(dc)[i] ], names(dc)[i] )
}
#new_names

dcn <- dc
names(dcn) <- new_names

run_reconstruction_table <- dcn


dcsum <- dc %>% filter(!a== 7) %>% group_by(i, b) %>% summarize( W = sum(W_star, na.rm=TRUE), harvest = sum(total_harvest_estimate, na.rm=TRUE), N = sum(N, na.rm=TRUE))


# Save run reconstruction data in a big table
usethis::use_data( run_reconstruction_table, overwrite = TRUE)


# Optional: merge result together into a big table. 

# Combine arrays function
# Create master table of all rates after QAQC
# function to combine arrays into data frame
# comb_arr <- function(x) {
# 
#   # Check list has names
#   if (is.null(names(x))) {
#     stop("List must be named.")
#   }
# 
#   # Convert each array to data frame using its list name
#   l_df <- Map(function(arr, nm) {
#     array2DF(arr, responseName = nm)
#   }, x, names(x))
# 
#   # Merge all data frames by the return year, age, and CU
#   combdf <- Reduce(function(d1, d2) {
#     merge(d1, d2, by = c("y", "a", "i"), all = TRUE)
#   }, l_df)
# 
#   combdf$y <- as.numeric(combdf$y)
#   combdf$a <- as.numeric(combdf$a)
#   combdf$b <- combdf$y - combdf$a # add brood year variable
#   return(combdf)
# }


```



```{r return, dpi=300}
ggplot( dcsum, aes(y = N, x = b)) +
  geom_line() +
  geom_hline(aes(yintercept=0)) +
  ylab(TeX("Skeena aggregate total run (black), wild\nspawners (blue), and harvest (red shaded)")) +
  xlab("Brood year") +
  geom_line( aes( y = W) , colour = "dodgerblue") + 
  geom_ribbon( aes( ymin = W, ymax = N), colour = NULL, fill= "red", alpha = 0.5) +
  facet_wrap( ~ i, scales = "free_y") +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5))


```

```{r harvest, dpi=300}
ggplot( dcsum, aes(y = harvest, x = b)) +
  geom_line() +
  geom_hline(aes(yintercept=0)) +
  ylab(TeX("Total harvest estimate")) +
  xlab("Brood year") +
  #geom_line( aes( y = W) , colour = "dodgerblue") + 
  facet_wrap( ~ i, scales = "free_y") +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.5))


```
